### 2023-10-27 README.qmd
Add link to renv:: and rebuild README
Move badge positions to top, add Zenodo badge and rerender

@@

1.  Clone or download [https://github.com/egouldo/this repository](https://github.com/egouldo/ManyEcoEvo)
2.  Run `renv::restore()` to load the packages used in the analysis pipeline locally on your machine
3.  Run `tar_destroy()` to remove any record and caches of existing targets
4.  Run `targets::tar_make()` in your console, depending on the power of your machine, the analysis pipeline will take between 2 and 7 minutes to execute (plus or minus some!)
5.  You can view a table of all targets in the pipeline by running `targets::tar_meta()`
6.  To interact with objects or 'targets' within the analysis pipeline, call `targest::tar_load()` or `targets::tar_read()`:

@@

This software is licensed with the GNU GPL 3 license [![License: GPL v3](https://img.shields.io/badge/License-GPLv3-blue.svg)](https://www.gnu.org/licenses/gpl-3.0)

@@

This package is released with a [Contributor Code of Conduct](https://github.com/egouldo/ManyEcoEvo/blob/aa2b9dcb6462f35ce873418e0b9c9697cf0b2f24/CODE_OF_CONDUCT.md) [![Contributor Covenant](https://img.shields.io/badge/Contributor%20Covenant-2.1-4baaaa.svg)](code_of_conduct.md)

>>>>

[![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.10046153.svg)](https://doi.org/10.5281/zenodo.10046153) [![License: GPL v3](https://img.shields.io/badge/License-GPLv3-blue.svg)](https://www.gnu.org/licenses/gpl-3.0) [![Contributor Covenant](https://img.shields.io/badge/Contributor%20Covenant-2.1-4baaaa.svg)](code_of_conduct.md)

@@

1.  Clone or download [https://github.com/egouldo/this repository](https://github.com/egouldo/ManyEcoEvo)
2.  Run `renv::restore()` to load the packages used in the analysis pipeline locally on your machine (see [`renv::`]https://rstudio.github.io/renv/index.html) for details)
3.  Run `tar_destroy()` to remove any record and caches of existing targets
4.  Run `targets::tar_make()` in your console, depending on the power of your machine, the analysis pipeline will take between 2 and 7 minutes to execute (plus or minus some!)
5.  You can view a table of all targets in the pipeline by running `targets::tar_meta()`
6.  To interact with objects or 'targets' within the analysis pipeline, call `targest::tar_load()` or `targets::tar_read()`:

@@

This software is licensed with the GNU GPL 3 license.

@@

This package is released with a [Contributor Code of Conduct](https://github.com/egouldo/ManyEcoEvo/blob/aa2b9dcb6462f35ce873418e0b9c9697cf0b2f24/CODE_OF_CONDUCT.md).
